Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-05-31 paper/src/dis.tex
Add more gap citations

The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}. As mentioned in the previous paragraph, our simulations do not support a strict gas dilution interpretation, but it was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G}. This gap is starvation-driven and can last several \Gyr{}. The present work argues for a starburst-driven quiescence followed by a rapid rejuvenation, with the entire process taking less than $1\,\Gyr$ and the gap only lasting a few hundred \Myr{}. The physical origin and some details are different, but one can appreciate that the bimodality arises from the same physical process.\footnote{Compare Section~\ref{ssec:formqui} to the first key result in the Conclusions of \citet{2024arXiv240511025S}.}

>>>>

The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}. As mentioned in the previous paragraph, our simulations do not support a strict gas dilution interpretation, but it was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G,2015A&A...578A..87S,2020A&A...640A..81N}. This gap is starvation-driven and can last several \Gyr{}. The present work argues for a starburst-driven quiescence followed by a rapid rejuvenation, with the entire process taking less than $1\,\Gyr$ and the gap only lasting a few hundred \Myr{}. The physical origin and some details are different, but one can appreciate that the bimodality arises from the same physical process.\footnote{Compare Section~\ref{ssec:formqui} to the first key result in the Conclusions of \citet{2024arXiv240511025S}.}
